MergeBiomarkWith10X

### 2022-01-18 MergeBiomarkWith10X/MergeBiomarkWith10X.Rmd
Minor change to document while in wrong brach

```{r}
pseudo.biomark.T[is.na(pseudo.biomark.T)] <- 0
pseudo.biomark.T <- as.sparse(pseudo.biomark.T)
biomark.object <- CreateSeuratObject(pseudo.biomark.T, project = "biomark", assay = "RNA", meta.data = biomark.meta)
```
## Thought experiment
```{r}
dbiomark.T <- data.table::transpose(dbiomark.data)
dbiomark.object <- CreateSeuratObject(dbiomark.T, project = "biomark", assay = "RNA", meta.data = biomark.meta)
```

>>>>

```{r}
pseudo.biomark.T[is.na(pseudo.biomark.T)] <- 0
pseudo.biomark.T <- as.sparse(pseudo.biomark.T)
biomark.object <- CreateSeuratObject(pseudo.biomark.T, project = "biomark", assay = "RNA", meta.data = biomark.meta)
```

## Thought experiment
```{r}
dbiomark.T <- data.table::transpose(dbiomark.data)
dbiomark.object <- CreateSeuratObject(dbiomark.T, project = "biomark", assay = "RNA", meta.data = biomark.meta)
```
